---
title: "Presentation Ninja"
subtitle: "xaringan"
author: "Yihui Xie"
date: "2016/12/12"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)

???

Image credit: [Wikimedia Commons](https://commons.wikimedia.org/wiki/File:Sharingan_triple.svg)

---
class: center, middle

# xaringan

### /ʃæ.'riŋ.ɡæn/

---
class: inverse, center, middle

# Get Started

---

# Yvette

.pull-left[
*Hillcrest*

Pros
* easy to get to 
* No early start to drive to
* Double lapper (which you know I love)
* Nice support on the route

Cons
* Hilly
* The laps can be split into two distinct sections - downhill and then uphill
* Very little relief on the course for your legs
* I drink too much beer after this race 
* Hard course to maintain a pace.
]

.pull-right[
**PMB**

Pros
* Nice route, undulating with some climbs but all doable and spread around the course
* Double lapper
* Fast finish home in case  you are chasing a time (except that stupid incline past the school)
* You can maintain a nice pace throughout the run

Cons
* Can be hot as hell
* Very early start if you don't stay up there
* Takes the whole weekend if you are staying up there
* I always think the course is easy, but it is not.
]

.footnote[[*] Not really. See next page.]


---

# Olly

Flip, not sure exactly what to tell you, I'm a fan of both the Hillcrest and the Maritzburg Marathon and both have played a key part in my Comrades training. They are both double lappers which I like, knowing what to expect for the second loop. I have run a faster Maritzburg (3:16) versus a Hillcrest (around 3:28 I think?) but I really gave the Maritzburg Marathon a real crack back then - my running ambitions have somewhat lowered since then! The key difference between the two is the last 7 or so kilometres - the tougher finish up Old Main Road at the Hillcrest compared to a fast finish at the Maritzburg Marathon. So if I had to choose, I would say perhaps the Maritzburg Marathon would be more conducive to a faster marathon simply based on the positioning of the climbs and at what stage of the marathon they appear. Both events are brilliantly organised.
 
If my training goes well, the annual plan is to qualify at the Hillcrest with a "C-Batch" sub-3:40 (running even splits) and then run a "comfortable"sub-4 hour at the Maritzburg Marathon two weeks later (also even splits).

---

# Karl

I enjoy both marathons, they are both relatively close to home and both manageable marathons for a novice.
Personally Hillcrest is nicer because as a Pinetown resident there is less distance to travel for the marathon(unless I sleep in PMB) and slightly more sleeping time.
I would say though in my experience that Hillcrest is tougher, the last 10 km hilly climb back to the finish is probably the main reason.
That being said there is a lot that can be done with all the down in km's 21 to 31.
If needed one can recover for the ups there after. If feeling strong one can make some very good time in this stretch too.
PMB is an undulating run with a few considerable hills, but most of these well over before the end of the race.
My faster time has been in PMB though, sub 4 mat to mat (4:01 gun to gun) as compared to 4:07 in Hillcrest.

---

1. Box plot of marathon time versus location (and possibly gender).
2. Fit lm and do ANOVA.
3. t-test across whole population.
4. Paired plots.
5. Fit lm.
6. Paired t-test.

---

```{r echo = FALSE}
library(readr)
library(dplyr)

marathons <- read_tsv("marathon-data.tsv", col_types = "cccic")

marathons <- rename(marathons, athlete = athlete_id, race = name) %>%
  mutate(
    # time -> decimal minutes
    time = as.integer(sub("000000$", "", time)) / 60,
    #
    race = factor(sub(" Marathon$", "", race)),
    athlete = factor(athlete)
  )

hillcrest = filter(marathons, race == "Hillcrest") %>% select(-race)
maritzburg = filter(marathons, race == "Maritzburg") %>% select(-race)

merged = merge(hillcrest, maritzburg, by = c("year", "athlete")) %>%
  rename(hillcrest = time.x, maritzburg = time.y) %>%
  mutate(difference = maritzburg - hillcrest)

# # Exclude 2010 data because it had a different cutoff time.
# #
# comparable_marathons = subset(marathons, year != 2010)
# 
# hillcrest = filter(comparable_marathons, race == "Hillcrest") %>% select(-race)
# maritzburg = filter(comparable_marathons, race == "Maritzburg") %>% select(-race)
```

---

# Time versus Race

```{r echo = FALSE}
library(ggplot2)

colour_hillcrest = "blue"
colour_maritzburg = "green"

marathon_colours <- c(colour_hillcrest, colour_maritzburg)

ggplot(marathons, aes(x = race, y = time / 60)) +
  geom_boxplot(aes(fill = race)) +
  scale_fill_manual(values = marathon_colours) +
  labs(x = "", y = "Hours") +
  theme_minimal() + theme(legend.position = "none")
```

```{r eval = FALSE}
devtools::install_github("yihui/xaringan")
```

---

# Time versus Race

```{r}
fit <- lm(time ~ race, data = marathons)
summary(fit)
```

---

```{r}
t.test(maritzburg$time, hillcrest$time)
```

---

```{r echo = FALSE, fig.height = 4, dev = 'svg'}
ggplot(merged, aes(x = hillcrest / 60, y = maritzburg / 60)) +
  geom_point(alpha = 0.25) +
  geom_smooth(method = "lm", formula = y ~ x) +
  geom_smooth(method = "lm", formula = y ~ x + 0, color = "red") +
  geom_abline(slope = 1, lty = "dashed") +
  labs(x = "Hillcrest [Hours]", y = "Maritzburg [Hours]") +
  theme_minimal()
```

---

```{r}
fit.1 <- lm(maritzburg ~ hillcrest, data = merged)
summary(fit.1)
```

---

```{r}
fit.0 <- lm(maritzburg ~ hillcrest + 0, data = merged)
summary(fit.0)
```

This model is more parsimonious.

---

```{r}
t.test(merged$maritzburg, merged$hillcrest, paired = TRUE)
```

---

```{r echo = FALSE, fig.height = 4, dev = 'svg'}
ggplot(merged, aes(x = difference)) +
  # geom_histogram() +
  geom_density(fill = "lightgrey", alpha = 0.5) +
  geom_vline(xintercept = 0, lty = "dashed") +
  labs(x = "Maritzburg - Hillcrest [Minutes]", y = "Density") +
  scale_x_continuous(limits = c(-150, 150)) +
  theme_minimal()
```

---
class: inverse, middle, center

# Using xaringan

---

# HTML Widgets

I have not thoroughly tested HTML widgets against **xaringan**. Some may work well, and some may not. It is a little tricky.

Similarly, the Shiny mode (`runtime: shiny`) does not work. I might get these issues fixed in the future, but these are not of high priority to me. I never turn my presentation into a Shiny app. When I need to demonstrate more complicated examples, I just launch them separately. It is convenient to share slides with other people when they are plain HTML/JS applications.

See the next page for two HTML widgets.

---

```{r out.width='100%', fig.height=6, eval=require('leaflet')}
library(leaflet)
leaflet() %>% addTiles() %>% setView(30.765, -29.805, zoom = 13)
```

---

```{r out.width='100%', fig.height=6, eval=require('leaflet')}
library(leaflet)
leaflet() %>% addTiles() %>% setView(30.385, -29.615, zoom = 12)
```

---

# Some Tips

- When you use the "Infinite Moon Reader" addin in RStudio, your R session will be blocked by default. You can click the red button on the right of the console to stop serving the slides, or use the _daemonized_ mode so that it does not block your R session. To do the latter, you can set the option

    ```r
    options(servr.daemon = TRUE)
    ```
    
    in your current R session, or in `~/.Rprofile` so that it is applied to all future R sessions. I do the latter by myself.
    
    To know more about the web server, see the [**servr**](https://github.com/yihui/servr) package.

--

- Do not forget to try the `yolo` option of `xaringan::moon_reader`.

    ```yaml
    output:
      xaringan::moon_reader:
        yolo: true
    ```

---

# Some Tips

- Slides can be automatically played if you set the `autoplay` option under `nature`, e.g. go to the next slide every 30 seconds (this can be useful for lightning talks):

    ```yaml
    output:
      xaringan::moon_reader:
        nature:
          autoplay: 30000
    ```

--

- The option `highlightLines: true` of `nature` will highlight code lines that start with `*` or are wrapped in `{{ }}`;

    ```yaml
    output:
      xaringan::moon_reader:
        nature:
          highlightLines: true
    ```

    See examples on the next page.

---

# Some Tips


.pull-left[
An example using a leading `*`:

    ```r
    if (TRUE) {
    ** message("Very important!")
    }
    ```
Output:
```r
if (TRUE) {
* message("Very important!")
}
```

This is invalid R code, so it is a plain fenced code block that is not executed.
]

.pull-right[
An example using `{{}}`:

    `r ''````{r tidy=FALSE}
    if (TRUE) {
    *{{ message("Very important!") }}
    }
    ```
Output:
```{r tidy=FALSE}
if (TRUE) {
{{ message("Very important!") }}
}
```

It is valid R code so you can run it.
]

---

# Some Tips

- To make slides work offline, you need to download a copy of remark.js in advance, because **xaringan** uses the online version by default (see the help page `?xaringan::moon_reader`).

- You can use `xaringan::summon_remark()` to download the latest or a specified version of remark.js. By default, it is downloaded to `libs/remark-latest.min.js`.

- Then change the `chakra` option in YAML to point to this file, e.g.

    ```yaml
    output:
      xaringan::moon_reader:
        chakra: libs/remark-latest.min.js
    ```

- If you used Google fonts in slides (the default theme uses _Yanone Kaffeesatz_, _Droid Serif_, and _Source Code Pro_), they won't work offline unless you download or install them locally. The Heroku app [google-webfonts-helper](https://google-webfonts-helper.herokuapp.com/fonts) can help you download fonts and generate the necessary CSS.


---

# CSS

Among all options in `xaringan::moon_reader`, the most challenging but perhaps also the most rewarding one is `css`, because it allows you to customize the appearance of your slides using any CSS rules or hacks you know.

You can see the default CSS file [here](https://github.com/yihui/xaringan/blob/master/inst/rmarkdown/templates/xaringan/resources/example.css). You can completely replace it with your own CSS files, or define new rules to override the default.

---

# CSS

For example, suppose you want to change the font for code from the default "Source Code Pro" to "Ubuntu Mono". You can create a CSS file named, say, `ubuntu-mono.css`:

```css
@import url(https://fonts.googleapis.com/css?family=Ubuntu+Mono:400,700,400italic);

.remark-code, .remark-inline-code { font-family: 'Ubuntu Mono'; }
```

Then set the `css` option in the YAML metadata:

```yaml
output:
  xaringan::moon_reader:
    css: ["default", "ubuntu-mono.css"]
```

Here I assume `ubuntu-mono.css` is under the same directory as your Rmd.

---
class: inverse, middle, center
background-image: url(https://upload.wikimedia.org/wikipedia/commons/3/39/Naruto_Shiki_Fujin.svg)
background-size: contain

# Naruto

---
background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)
background-size: 100px
background-position: 90% 8%

# Sharingan

The R package name **xaringan** was derived<sup>1</sup> from **Sharingan**, a dōjutsu in the Japanese anime _Naruto_ with two abilities:

- the "Eye of Insight"

- the "Eye of Hypnotism"

I think a presentation is basically a way to communicate insights to the audience, and a great presentation may even "hypnotize" the audience.<sup>2,3</sup>

.footnote[
[1] In Chinese, the pronounciation of _X_ is _Sh_ /ʃ/ (as in _shrimp_). Now you should have a better idea of how to pronounce my last name _Xie_.

[2] By comparison, bad presentations only put the audience to sleep.

[3] Personally I find that setting background images for slides is a killer feature of remark.js. It is an effective way to bring visual impact into your presentations.
]

---

# Naruto terminology

The **xaringan** package borrowed a few terms from Naruto, such as

- [Sharingan](http://naruto.wikia.com/wiki/Sharingan) (写輪眼; the package name)

- The [moon reader](http://naruto.wikia.com/wiki/Moon_Reader) (月読; an attractive R Markdown output format)

- [Chakra](http://naruto.wikia.com/wiki/Chakra) (查克拉; the path to the remark.js library, which is the power to drive the presentation)

- [Nature transformation](http://naruto.wikia.com/wiki/Nature_Transformation) (性質変化; transform the chakra by setting different options)

- The [infinite moon reader](http://naruto.wikia.com/wiki/Infinite_Tsukuyomi) (無限月読; start a local web server to continuously serve your slides)

- The [summoning technique](http://naruto.wikia.com/wiki/Summoning_Technique) (download remark.js from the web)

You can click the links to know more about them if you want. The jutsu "Moon Reader" may seem a little evil, but that does not mean your slides are evil.

---

class: center

# Hand seals (印)

Press `h` or `?` to see the possible ninjutsu you can use in remark.js.

![](https://upload.wikimedia.org/wikipedia/commons/7/7e/Mudra-Naruto-KageBunshin.svg)

---

class: center, middle

# Thanks!

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).

The chakra comes from [remark.js](https://remarkjs.com), [**knitr**](http://yihui.name/knitr), and [R Markdown](https://rmarkdown.rstudio.com).
