---
title: "Untitled"
output:
  revealjs::revealjs_presentation:
    theme: sky
    highlight: haddock
    center: true
    transition: fade
    reveal_options:
      slideNumber: true
      previewLinks: true
---

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Olly

Flip, not sure exactly what to tell you, I’m a fan of both the Hillcrest and the Maritzburg Marathon and both have played a key part in my Comrades training. They are both double lappers which I like, knowing what to expect for the second loop. I have run a faster Maritzburg (3:16) versus a Hillcrest (around 3:28 I think?) but I really gave the Maritzburg Marathon a real crack back then – my running ambitions have somewhat lowered since then! The key difference between the two is the last 7 or so kilometres – the tougher finish up Old Main Road at the Hillcrest compared to a fast finish at the Maritzburg Marathon. So if I had to choose, I would say perhaps the Maritzburg Marathon would be more conducive to a faster marathon simply based on the positioning of the climbs and at what stage of the marathon they appear. Both events are brilliantly organised.
 
If my training goes well, the annual plan is to qualify at the Hillcrest with a “C-Batch” sub-3:40 (running even splits) and then run a “comfortable”sub-4 hour at the Maritzburg Marathon two weeks later (also even splits).

## Yvette

Hillcrest PRo's

easy to get to 
No early start to drive to
Double lapper (which you know I love)
Nice support on the route

Con’s

Hilly
The laps can be split into two distinct sections – downhill and then uphill
Very little relief on the course for your legs
I drink too much beer after this race 
Hard course to maintain a pace.

PMB Pros

Nice route, undulating with some climbs but all doable and spread around the course
Double lapper
Fast finish home in case  you are chasing a time (except that stupid incline past the school)
You can maintain a nice pace throughout the run

Con’s

Can be hot as hell
Very early start if you don’t stay up there
Takes the whole weekend if you are staying up there
I always think the course is easy, but it is not.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

